\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage[margin=0.7in]{geometry}%
\usepackage{parskip}%
\usepackage{setspace}%
\usepackage{enumitem}%
\setstretch{0.88}%
%
\setcounter{secnumdepth}{0}%
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}%
\title{Lucy C. Murray}%
\date{}%
%
\begin{document}%
\normalsize%
\maketitle%
\section{Contact Information}%
\label{sec:ContactInformation}%
\textbf{Email: } lcmurray37@gmail.com\\%
\textbf{Phone: } (202) 934-3066\\%
\textbf{GitHub: } github.com/lcmurray37\\

%
\section{Professional Summary}%
\label{sec:ProfessionalSummary}%
\begin{itemize}%
\item Versatile Data Science and Information Management professional with 7+ years of experience leading enterprise analytics, data engineering, and database modernization.%
\item Led cross-functional teams of 14+ members delivering scalable data pipelines and cloud analytics tools.%
\item Bridges technical execution with executive strategy to drive data-informed decision making.%
\end{itemize}

%
\section{Experience}%
\label{sec:Experience}%
\subsection{TECHNOMICS, INC. | Senior Analyst | Aug 2021 – Present}%
\label{subsec:TECHNOMICS,INC.|SeniorAnalyst|Aug2021Present}%
\textbf{Project Management & Leadership:}\\%
\begin{itemize}%
\item Led enterprise data science and analytics initiatives for federal, defense, and international clients.%
\item Managed Agile/Kanban teams of up to 14+ members.%
\item Directed sprint planning, code reviews, and technical mentorship.%
\end{itemize}%
\textbf{Data Science & Engineering:}\\%
\begin{itemize}%
\item Migrated legacy MS Access systems to DuckDB and R-based pipelines.%
\item Optimized SQL/R queries and validated data pipelines for modeling accuracy.%
\item Built prioritization models using Python and Palantir Foundry.%
\item Automated Excel-heavy reporting workflows using R and Python.%
\item Implemented Git/GitLab version-controlled data extraction workflows.%
\item Developed BI dashboards tracking cost growth and engineering change trends.%
\end{itemize}%
\textbf{Training & Organizational Impact:}\\%
\begin{itemize}%
\item Led Data & Analytics certification program for ~1,200 personnel.%
\item Developed training modules in statistical sampling and enterprise data systems.%
\end{itemize}

%
\subsection{KCIC, LLC | Senior Data Analyst | Mar 2019 – Aug 2021}%
\label{subsec:KCIC,LLC|SeniorDataAnalyst|Mar2019Aug2021}%
\textbf{Database Engineering & Analytics:}\\%
\begin{itemize}%
\item Built optimized SQL views, stored procedures, and indexes improving query performance.%
\item Developed SQL + Excel reporting pipelines for large claims datasets.%
\item Designed validation systems ensuring data integrity under strict deadlines.%
\end{itemize}%
\textbf{Process Improvement & Training:}\\%
\begin{itemize}%
\item Standardized analytics training programs across analyst teams.%
\end{itemize}

%
\section{Education}%
\label{sec:Education}%
\begin{itemize}%
\item Professional Certificate in Data Science — Montgomery College (2019–2020)%
\item B.A. Economics, Government & Politics — University of Maryland (2013–2017)%
\end{itemize}

%
\section{Core Competencies}%
\label{sec:CoreCompetencies}%
\textbf{Leadership: } Agile, Kanban, Project Management, Stakeholder Engagement\\%
\textbf{Data Science: } Python, R, Statistical Modeling, Visualization\\%
\textbf{Data Engineering: } SQL, ETL/ELT, DuckDB, MongoDB\\%
\textbf{Tools: } Power BI, Git, Excel, Palantir Foundry\\

%
\end{document}